Setting up Data

### 2020-04-26 src/SetupData.Rmd
wrote main column names to the main MLH1 file

- rm Peromycus data BivData!!

- code Mol as discint subsp

- make sure to remove some of the juvi mice!! from the AP_mouse table

@@

MLH1_data = read.csv(here("data", "/MLH1/AnonData.csv"), header=TRUE)

@@

Curated_BivData$Rec.group <- ifelse(grepl("PWD male", Curated_BivData$category), 1, 
                              ifelse(grepl("MSM male", Curated_BivData$category), 1,
                                ifelse(grepl("SKIVE male", Curated_BivData$category), 1, 0)))

Curated_BivData$Rec.group_alt <- ifelse(grepl("PWD male", Curated_BivData$category), 1, 
                              ifelse(grepl("MSM male", Curated_BivData$category), 1, 0))
```

@@

#make the table with ALL MLH1 obs

FULL_mouse_table_MLH1 <- ddply(MLH1_data, c("mouse"), summarise,

@@

@@

save.image("~./MLH1repo/data/MLH1/MLH1_data_setup_4.21.20.RData")

>>>>

@@

MLH1_data = read.csv(here("data", "/AnonData_formated.csv"), header=TRUE)

@@

#Curated_BivData$Rec.group <- ifelse(grepl("PWD male", Curated_BivData$category), 1, 
#                              ifelse(grepl("MSM male", Curated_BivData$category), 1,
#                                ifelse(grepl("SKIVE male", Curated_BivData$category), 1, 0)))

#Curated_BivData$Rec.group_alt <- ifelse(grepl("PWD male", Curated_BivData$category), 1, 
#                              ifelse(grepl("MSM male", Curated_BivData$category), 1, 0))
```

@@

#make the table with ALL MLH1 obs
FULL_mouse_table_MLH1 <- ddply(MLH1_data, c("mouse"), summarise,

@@

Number of cells per mouse, (were any mice excluded for low numbers of cells?) (were all cells pooled?)

@@

save.image("~./MLH1repo/data/MLH1/MLH1_data_setup_4.26.20.RData")
